---
title: "Presentation"
author: "Group"
date: "4/20/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
library(magrittr)
library(tidyr)

full_data <-  read.csv("Dataset/cleaned_data.csv")
data <- full_data %>%
  drop_na
```

## Introduction

* Description

* Research Question:

    **Which characteristics of Electric Vehicles have a significant impact on their price?**

## Data Description

## Word Cloud
```{r, echo = FALSE, message = FALSE, warning = FALSE}
full_data %<>%
  separate(
    Name,
    "Manufacturer",
    extra = "drop",
    remove = F
  )

frequency <- full_data %>% 
  group_by(Manufacturer) %>% 
  count(Manufacturer,sort=T) %>% 
  ungroup()

library(wordcloud)
wordcloud(words = frequency$Manufacturer, freq = frequency$n,min.freq=1,max.words=100, random.order=FALSE, rot.per=0.35,colors=brewer.pal(10, "Dark2"))
```

## Bar Chart
```{r, echo = FALSE, message = FALSE, warning=FALSE}
data %>% 
  top_n(20) %>%
  ggplot(aes(x=TopSpeed,
             y=reorder(Name,TopSpeed),
             fill=TopSpeed)) + 
  geom_col(show.legend = FALSE) +
  geom_text(aes(label=TopSpeed),
            position = position_dodge(width = 0.9),
            hjust= 1, color = "white") +
  labs(x = "", y = "")
```

## Correlation Matrix
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(heatmaply)

palette = colorRampPalette(c("green", "white", "red")) (20)
cor_data <- full_data %>%
  select_if(is.numeric) %>%
  cor(use = "pairwise")
corrplot::corrplot(cor_data, method = "number",bg="white",col = palette,tl.col="black",
                   number.cex = 0.75)
```

## Process
<!-- Add model comparison stuff with: -->
<!-- full and reduced model -->
<!-- transformed and not transformed predictors -->
<!-- transformed and not transformed response -->

## Full (Untransformed) Model Diagnostics
```{r, echo=FALSE}
full_model <- (
  PriceinUK ~
    Subtitle +
    Range +
    Acceleration + 
    TopSpeed +
    Efficiency +
    FastChargeSpeed +
    NumberofSeats 
) %>%
  lm(data)

full_model$residuals %>% shapiro.test()
full_model %>% (lmtest::bptest)
```

## Full (Semitransformed) Model Diagnostics
```{r, echo=FALSE}
full_model <- (
  PriceinUK ~
    log(Subtitle) +
    log(Range) +
    poly(Acceleration, 2, raw = T) + 
    poly(TopSpeed, 2, raw = T) +
    poly(Efficiency, 2, raw = T) +
    FastChargeSpeed +
    NumberofSeats 
) %>%
  lm(data)

full_model$residuals %>% shapiro.test()
full_model %>% (lmtest::bptest)
```

## Full (Transformed) Model Diagnostics
```{r, echo=FALSE}
full_model <- (
  1 / sqrt(PriceinUK) ~
    log(Subtitle) +
    log(Range) +
    poly(Acceleration, 2, raw = T) + 
    poly(TopSpeed, 2, raw = T) +
    poly(Efficiency, 2, raw = T) +
    FastChargeSpeed +
    NumberofSeats 
) %>%
  lm(data)

full_model$residuals %>% shapiro.test()
full_model %>% (lmtest::bptest)
```

## Final Model
$$
\begin{align*}
\frac{1}{\sqrt{\texttt{PriceinUK}}} &= \beta_0 \\
&+ \beta_1 \ln \texttt{Range} \\
&+ \beta_2 \texttt{Acceleration} + \beta_3 \texttt{Acceleration}^2 \\
&+ \beta_4 \texttt{TopSpeed} + \beta_5 \texttt{TopSpeed}^2 \\
&+ \beta_6 \texttt{Efficiency} + \beta_7\texttt{Efficiency}^2\\
&+ \beta_8 \texttt{NumberofSeats} \\
&+ \epsilon
\end{align*}
$$

## Results
```{r, echo=FALSE}
final_model <- (
    1 / sqrt(PriceinUK) ~
      log(Range) +
      #poly(Acceleration, 2, raw = T) + 
      poly(TopSpeed, 2, raw = T) +
      poly(Efficiency, 2, raw = T)# +
      #NumberofSeats
) %>%
  lm(data)

coefficient_tab <- final_model %>%
  summary %$%
  coefficients

coefficient_tab %>%
  kable
```

## Residuals vs Fitted Values Plot
```{r, echo=FALSE, message=FALSE, warning=FALSE}
std_residuals <- final_model %>%
  rstandard

plot(final_model, which = 1)
# ggplot(
#   mapping = aes(
#     x = final_model$fitted.values,
#     y = final_model$residuals,
#   )
# ) +
#   geom_point(aes(color = std_residuals %>% abs > 2)) +
#   geom_smooth(se = F) +
#   labs(
#     x = "Fitted Values",
#     y = "Residuals",
#     color = "High Standardized\nResidual\n(absolute value > 2)"
#   )
```

## Q-Q Plot
```{r, echo=FALSE}
ggplot(mapping = aes(sample = std_residuals)) +
  geom_qq() +
  geom_qq_line() +
  labs(
    x = "Theorhetical Quantiles",
    y = "Standardized Residuals"
  )
```

## Assumptions Tests
```{r, echo=FALSE}
std_residuals %>% shapiro.test
final_model %>% (lmtest::bptest)
```

## Outliers
Here, outlier was defined as points that were both high leverage and high residual.

```{r}
leverage <- final_model %>% hatvalues
high_leverage <- abs(leverage) > 2*mean(leverage)
high_residal <- abs(std_residuals) > 2
data %>%
  subset(
    high_leverage & high_residal,
    c("Name", "PriceinUK")
  ) %>%
  kable
```

## Testing
<!-- Possibly merge with next slide to avoid confusion -->
```{r, echo=FALSE}

# This is where I filled in some of the NAs
found_ind <- c(5, 7, 9, 12, 18, 22, 28, 29, 35, 36, 42, 44)
found_prices <- c(22585, 35050, 28950, 34995, 48335, 49105, 72175, 73785, 51510, 53010, 54990, 48280)
full_data[found_ind, "PriceinUK"] <- found_prices

# test_data <- anti_join(full_data, data, by = "Name") %>%
#   select(
#     Name,
#     PriceinUK,
#     Range,
#     #Acceleration,
#     TopSpeed,
#     Efficiency,
#     NumberofSeats
#   ) %>%
#   drop_na

n <- nrow(full_data)
set.seed(96000)
test_data <- data[sample(n, 10), ] %>%
  select(
    Name,
    PriceinUK,
    Range,
    TopSpeed,
    Efficiency,
    NumberofSeats
  ) %>%
  drop_na

test <- test_data$PriceinUK
inv_sq_test <- test^(-2)
pred_inv_sq_test <- final_model %>% predict(test_data)
pred_test <- pred_inv_sq_test^(-2)

ggplot(
  mapping = aes(inv_sq_test, pred_inv_sq_test)
) +
  geom_abline(slope = 1, intercept = 0) +
  geom_point() +
  labs(
    x = "PriceinUK^(-0.5)",
    y = "Predicted PriceinUK^(-0.5)"
  )
```

## Prediction Error
```{r, echo=FALSE, message=FALSE}
library(caret)
data.frame(
  prediction = c(
    "`1 / sqrt(PriceinUK)`",
    "`PriceinUK`"
  ),
  R2 = c(
    R2(pred_inv_sq_test, inv_sq_test),
    R2(pred_test, test)
  ),
  MAE = c(
    MAE(pred_inv_sq_test, inv_sq_test),
    MAE(pred_test, test)
  ),
  RMSE = c(
    RMSE(pred_inv_sq_test, inv_sq_test),
    RMSE(pred_test, test)
  )
) %>%
  kable
```
## Conclusion